FinalManuscript_DISCS_UG

### 2019-02-18 pcsc-paper/parts/05__00_experiments.tex
Time graphs

We first summarize the approximations discussed in Sections \ref{sec:logarithm_approximation} and \ref{sec:arctan_approximation} in Table \ref{tab:approximation_summary}.

>>>>

We first summarize the approximations discussed in Sections~\ref{sec:logarithm_approximation} and~\ref{sec:arctan_approximation} in Table~\ref{tab:approximation_summary}.

### 2019-02-18 pcsc-paper/parts/05_testsforaccuracy.tex
Time graphs

>>>>

\subsection{Timing Results}

\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			% xmin=0, xmax=255,
			ytick={1,2},
			yticklabels={Scaled quadrature, Original quadrature},
			xlabel={Time (seconds)},
			grid=major,
			legend pos=north east,
			legend cell align=left,
		]
		\addplot+[boxplot, thick, ACMDarkBlue] table[x=x, y=newt] {plots/comp_log_errs.txt};
		\addplot+[boxplot, thick, ACMOrange] table[x=x, y=oldt] {plots/comp_log_errs.txt};
		\end{axis}
	\end{tikzpicture}%
	\caption{Comparison of logarithm computation times under Paillier}
	\label{fig:times_log}
\end{figure}

\begin{figure}[!ht]
	\centering
	\begin{tikzpicture}
		\begin{axis}[
			% xmin=0, xmax=255,
			ytick={1,2},
			yticklabels={Gauss--Legendre quadrature, Euler's series},
			xlabel={Time (seconds)},
			grid=major,
			legend pos=north east,
			legend cell align=left,
		]
		\addplot+[boxplot, thick, ACMDarkBlue] table[x=x, y=newt] {plots/comp_arctan_errs2.txt};
		\addplot+[boxplot, thick, ACMOrange] table[x=x, y=oldt] {plots/comp_arctan_errs2.txt};
		\end{axis}
	\end{tikzpicture}%
	\caption{Frequency distribution of inverse tangent computation times under Paillier}
	\label{fig:times_arctan}
\end{figure}

% \begin{figure}[!ht]
% 	\centering
% 	\begin{tikzpicture}
% 		\begin{axis}[
% 			xmin=0, xmax=1,
% 			ymin=1.5, ymax=2.5,
% 			xlabel={Absolute error}, ylabel={Time (seconds)},
% 			grid=major,
% 			legend pos=south east,
% 			legend cell align=left,
% 			tick scale binop=\times,
% 		]
% 		\addplot+[scatter, only marks, ACMDarkBlue] table[x=newerr, y=newt] {plots/comp_arctan_errs2.txt};
% 		\addplot+[scatter, only marks, ACMOrange] table[x=olderr, y=oldt] {plots/comp_arctan_errs2.txt};
% 		\legend{Gauss--Legendre quadrature, Partial sum of Euler's series}
% 		\end{axis}
% 	\end{tikzpicture}%
% 	\caption{Accuracy vs. time in inverse tangent computation under Paillier}
% 	\label{fig:acc_vs_time_arctan}
% \end{figure}
